---
title: "latent Dirichlet allocation"
output: html_notebook
---
 Applying Latent Dirichlet allocation in order to find the most important topic groups in Netflix Tweets 


```{r}
if (!require("pacman")) install.packages("pacman") ; require("pacman")
p_load(tidyverse, topicdoc, topicmodels, tm, textcat, rlang, tidytext, ggmap)
p_load(tidyverse, rtweet, httpuv, stringr, qdap, httr, wordcloud2, tm, tidytext, wordcloud)

```
```{r}
tweets %>% glimpse() 
#only use the text from the tweets 
text <- tweets_data(tweets) %>% pull(text)

```



```{r}
#develop model on smaller data set 

set.seed(123)
sample <- sample(unique(text), 
                              round(length(unique(text))/100), 
                              replace = FALSE)
length(sample)
```


```{r}
#applying pre processing to the smaller sample 
myCorpus <- Corpus(VectorSource(sample)) %>%
  tm_map(content_transformer(str_to_lower)) %>%
  tm_map(removePunctuation) %>%
  tm_map(removeNumbers) %>%
  tm_map(stripWhitespace)
myStopwords <- c(stopwords('english'))
myCorpus <- tm_map(myCorpus, removeWords, myStopwords)

```
```{r}
dtm1 <- DocumentTermMatrix(myCorpus)
dtm1 
```


```{r}
```


```{r}
```


```{r}
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

